---
title: "Lab 01 - Hello R"
author: "Lindsay Stall"
date: "1/13/2023"
output: 
  html_document: 
    theme: cerulean
    fig_width: 6
    fig_height: 6
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

A data frame with 1846 rows and 3 variables:

dataset: indicates which dataset the data are from

x: x-values

y: y-values.

### Exercise 2

Plot y vs. x for the dino dataset. Then, calculate the correlation coefficient between x and y for this dataset.

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x, y)) +
  geom_point()
```

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(y, x)) +
  geom_point()
```

The correlation for this plot is nearly identical to the dino plot.

```{r cor-star}
star_data %>%
  summarize(r = cor(y, x))
```

### Exercise 4

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(y, x)) +
  geom_point()
```

```{r cor-circle}
circle_data %>%
  summarize(r = cor(y, x))
```

The correlation of the circle data is slightly stronger than dino, but they are basically the same.

### Exercise 5

Add code and narrative as needed.

To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```
